---
title: 'Domain-general cognitive motivation: evidence from economic decision-making'
author: "Jennifer L. Crawford"
date: "8/24/2021"
output:
  html_document:
    df_print: paged
---
## Summary of findings from online data collection for multi-domain discounting project
### 104 Younger adult participants

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

#Packages
library(brms); library(bayestestR); library(BayesFactor); library(correlation); library(knitr);
library(RColorBrewer); library(tidyverse);
source("summarySEwithin2.R")

#Package versions used to run the analyses reported in the manuscript
##R version 4.1.0
##BayesFactor_0.9.12-4.2, bayestestR_0.10.5, brms_2.16.1, correlation_0.6.1, knitr_1.33,
##RColorBrewer_1.1-2, tidyverse_1.3.1

#Create data directories
#Cog-ED
coged.wm.path<-"https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Discounting/MDD_WMCogED_share.csv"
coged.wm.full.path <-"https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Discounting/MDD_WMCogED_full_share.csv"
coged.speech.path<-"https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Discounting/MDD_SpeechCogED_share.csv"
#Individual Difference Questionnaires
NCS.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Individual-Difference-Questionnaires/MDD_NCS_share.csv"
SPSRQ.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Individual-Difference-Questionnaires/MDD_SPSRQ_share.csv"
BISBAS.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Individual-Difference-Questionnaires/MDD_BISBAS_share.csv"
GRAPES.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Individual-Difference-Questionnaires/MDD_GRAPES_share.csv"
#Working Memory Capacity
LSpan.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Working-Memory-Capacity/MDD_LSpan_share.csv"
OSpan.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Working-Memory-Capacity/MDD_OSpan_share.csv"
SymmSpan.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Working-Memory-Capacity/MDD_SSpan_share.csv"
#complete subject list
subjects.path <- "https://raw.githubusercontent.com/jlcrawford/MDD/master/Data/Online/Discounting/subjects_online_MDD.csv"
#Make data frames for Cog-ED(s)
coged.wm<- read.csv(coged.wm.path, header = T)
coged.wm.full <- read.csv(coged.wm.full.path, header = T)
coged.speech<- read.csv(coged.speech.path, header = T) 
#Make data frames for individual difference questionnaires 
NCS <- read.csv(NCS.path, header = T)
SPSRQ <- read.csv(SPSRQ.path, header = T)
BISBAS <- read.csv(BISBAS.path, header = T)
GRAPES <- read.csv(GRAPES.path, header = T)
#Make data frames for working memory capacity tasks
LSpan <- read.csv(LSpan.path, header = T)
OSpan <- read.csv(OSpan.path, header = T)
SymmSpan <- read.csv(SymmSpan.path, header = T)
#Make data frame for usable subject info (i.e., subjects who have completed all tasks and questionnaires across both visits)
Subjects <- read.csv(subjects.path, header = F)
colnames(Subjects) <- "subjectid"
```

## Cognitive Effort Discounting
### Testing for the effects of task load and domain (e.g., working memory, speech) on subjective value

```{r SV_CogED, warning=F, message=F}
#Cog-ED Data
#clean data frame(s) with Cog-ED subjective value (SV) estimates and transform data so that SV estimates are equivalent
#across both domains (i.e., speech, WM)

##working memory
d.coged.wm <- coged.wm %>% select(subjectid,completed,fixedAmount_N2_1,fixedAmount_N2_2,fixedAmount_N2_3,
                            fixedAmount_N3_1,fixedAmount_N3_2,fixedAmount_N3_3,fixedAmount_N4_1,
                            fixedAmount_N4_2,fixedAmount_N4_3,
                            IP12_1,IP12_2,IP12_3,IP13_1,IP13_2,IP13_3,IP14_1,IP14_2,IP14_3) %>%
  filter(completed == 1) %>%
  group_by(subjectid) %>%
  mutate(Domain = "WM",
         domainCode = 0,
         SV2_1 = ifelse(fixedAmount_N2_1 == "X", IP12_1/2, ((2-IP12_1)/2)+1),
         SV2_2 = ifelse(fixedAmount_N2_2 == "X", IP12_2/3, ((3-IP12_2)/3)+1),
         SV2_3 = ifelse(fixedAmount_N2_3 == "X", IP12_1/4, ((4-IP12_3)/4)+1),
         SV3_1 = ifelse(fixedAmount_N3_1 == "X", IP13_1/2, ((2-IP13_1)/2)+1),
         SV3_2 = ifelse(fixedAmount_N3_2 == "X", IP13_2/3, ((3-IP13_2)/3)+1),
         SV3_3 = ifelse(fixedAmount_N3_3 == "X", IP13_1/4, ((4-IP13_3)/4)+1),
         SV4_1 = ifelse(fixedAmount_N4_1 == "X", IP14_1/2, ((2-IP14_1)/2)+1),
         SV4_2 = ifelse(fixedAmount_N4_2 == "X", IP14_2/3, ((3-IP14_2)/3)+1),
         SV4_3 = ifelse(fixedAmount_N4_3 == "X", IP14_3/4, ((4-IP14_3)/4)+1),
         SV_red = (SV2_1 + SV2_2 + SV2_3)/3,
         SV_blue = (SV3_1 + SV3_2 + SV3_3)/3,
         SV_purple = (SV4_1 + SV4_2 + SV4_3)/3)

##speech comprehension
d.coged.speech <- coged.speech %>%
  select(subjectid,completed,fixedAmount_N2_1,fixedAmount_N2_2,fixedAmount_N2_3,fixedAmount_N3_1,
                            fixedAmount_N3_2,fixedAmount_N3_3,fixedAmount_N4_1,
                            fixedAmount_N4_2,fixedAmount_N4_3,
                            IP12_1,IP12_2,IP12_3,IP13_1,IP13_2,IP13_3,IP14_1,IP14_2,IP14_3) %>%
  filter(completed == 1) %>%
  group_by(subjectid) %>%
  mutate(Domain = "Speech",
         domainCode = 1,
         SV2_1 = ifelse(fixedAmount_N2_1 == "X", IP12_1/2, ((2-IP12_1)/2)+1),
         SV2_2 = ifelse(fixedAmount_N2_2 == "X", IP12_2/3, ((3-IP12_2)/3)+1),
         SV2_3 = ifelse(fixedAmount_N2_3 == "X", IP12_1/4, ((4-IP12_3)/4)+1),
         SV3_1 = ifelse(fixedAmount_N3_1 == "X", IP13_1/2, ((2-IP13_1)/2)+1),
         SV3_2 = ifelse(fixedAmount_N3_2 == "X", IP13_2/3, ((3-IP13_2)/3)+1),
         SV3_3 = ifelse(fixedAmount_N3_3 == "X", IP13_1/4, ((4-IP13_3)/4)+1),
         SV4_1 = ifelse(fixedAmount_N4_1 == "X", IP14_1/2, ((2-IP14_1)/2)+1),
         SV4_2 = ifelse(fixedAmount_N4_2 == "X", IP14_2/3, ((3-IP14_2)/3)+1),
         SV4_3 = ifelse(fixedAmount_N4_3 == "X", IP14_3/4, ((4-IP14_3)/4)+1),
         SV_red = (SV2_1 + SV2_2 + SV2_3)/3,
         SV_blue = (SV3_1 + SV3_2 + SV3_3)/3,
         SV_purple = (SV4_1 + SV4_2 + SV4_3)/3)

#Merge WM and Speech Cog-ED data frames
coged.merged <- rbind(d.coged.wm, d.coged.speech)

#Filter out subjects who have not completed all tasks in the protocol
coged.merged <-inner_join(Subjects, coged.merged)

#Add dummy variables (task, domain) for multilevel models
d.coged.SV <- coged.merged %>% select(subjectid,Domain,domainCode, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid,Domain,domainCode)) %>%
  separate(col = tmp, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c("red","blue","purple"), labels=c(-1,0,1)))
d.coged.SV$taskCode <- as.numeric(d.coged.SV$taskCode)
d.coged.SV$domainCode <- as.numeric(d.coged.SV$domainCode)
#Multilevel model of subjective value with task and domain as predictors
m.SV.coged <- brm(data = d.coged.SV, SV ~ taskCode*domainCode + (1 | subjectid),
file = "models/m.SV.coged.rds")
summary(m.SV.coged)
bayes_R2(m.SV.coged)
```

## Plotting SV estimates across working memory and speech comprehension domains
## Figure 1

```{r CogED_Plot, warning = F, message = F}
#Plotting SV estimates
#Create summary stats for group plots
CogED_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Domain"),
                              idvar = "subjectid")
CogED_sum$Task <- factor(CogED_sum$Task, levels = c("red","blue","purple"),
                         labels = c("red","blue","purple"))
CogED_sum$Domain <- factor(CogED_sum$Domain, levels = c("WM","Speech"), 
                           labels = c("WM","Speech"))

#Plotting SV across both gain and loss domains
##Create domain labels
Domain.labs <- c("Speech Comprehension", "Working Memory")
names(Domain.labs) <- c("Speech", "WM")

#Figure 1
##Subjective value estimates across working memory and speech comprehension domains
###Low effort = 2-back; -4 SNR, Medium effort = 3-back;-8 SNR, High effort = 4-back;-12 SNR
fig.1 <- ggplot(CogED_sum, aes(x=Task, y=SV, fill=Task, color=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold",
        size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2, size=1.25) +  
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") +
  facet_wrap(.~ Domain, labeller = labeller(Domain = Domain.labs))
fig.1 + scale_fill_brewer(palette = "Set1",  name="Task Effort Level", labels=c("Low","Medium","High")) + 
  scale_color_brewer(palette = "Set1", name="Task Effort Level",labels=c("Low","Medium","High"))
```

## Stage I of Analysis: Zero-order correlation between average subjective value across working memory and speech comprehension domains

```{r CogED_cor, warning = F, message = F}
#Correlating Average SV (within-subject) across working memory and speech comprehesion domains
##Creating data frame with SV estimates across both domains
average.SV <- coged.merged %>% select(subjectid, Domain, SV_red, SV_blue, SV_purple) %>%
  group_by(subjectid, Domain) %>%
  dplyr::summarise(SV_avg = (SV_red + SV_blue + SV_purple)/3) %>%
  pivot_wider(values_from = "SV_avg", names_from = "Domain")

#T-tests between average SV estimates across WM and speech domains
##Average across all effort levels
SV.t <- t.test(x= average.SV$WM, y= average.SV$Speech, paired = TRUE)
SV.t
SV.BF <- ttestBF(x= average.SV$WM, y= average.SV$Speech, paired = TRUE)
SV.BF

#Low effort (2-back; -4SNR)
SV.red.t <- t.test(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="red"],
                   y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="red"],
                   paired = TRUE)
SV.red.t
SV.red.BF <- ttestBF(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="red"],
                     y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="red"],
                     paired = TRUE)
summary(SV.red.BF)

#Medium effort (3-back; -8 SNR)
SV.blue.t <- t.test(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="blue"],
                    y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="blue"],
                    paired = TRUE)
SV.blue.t
SV.blue.BF <- ttestBF(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="blue"],
                      y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="blue"],
                      paired = TRUE)
summary(SV.blue.BF)

#High effort (4-back; -12SNR)
SV.purple.t <- t.test(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="purple"],
                      y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="purple"],
                      paired = TRUE)
SV.purple.t
SV.purple.BF <- ttestBF(x= d.coged.SV$SV[d.coged.SV$Domain=="WM" & d.coged.SV$Task=="purple"],
                        y= d.coged.SV$SV[d.coged.SV$Domain=="Speech" & d.coged.SV$Task=="purple"],
                        paired = TRUE)
summary(SV.purple.BF)

#Testing for correlation between cognitive effort discounting across working memory & speech domains
CogED.cor <- cor_test(data = average.SV, x = "Speech", y = "WM", bayesian = TRUE, bayesian_prior = 0.707107)
#Summarize Bayes Factor from correlation
CogED.cor

#Plot of correlation between working memory & speech comprehension domains
##Not included in manuscript
fig.corr <- ggplot(average.SV, aes(Speech, WM)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(), panel.background = element_blank(),
         axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Speech Comprehension") + ylab("Working Memory")
fig.corr
```

## Stage II of Analysis: Partialing out task level and performance on subjective value estimates
### Familiarization Phase Performance
### Speech
```{r Familiarization_Speech, warning = F, message = F}
#Summarizing intelligibility ratings across all speech-in-noise task levels
performance.speech <- coged.speech %>% select(subjectid, completed, percentCorrect_N1, percentCorrect_N2, percentCorrect_N3, percentCorrect_N4) %>%
   group_by(subjectid) %>% filter(completed == 1) %>% select(-completed) %>%
  pivot_longer(names_to = "level", values_to = "performance", -c(subjectid)) %>%
  separate(col = level, into=c(NA,"Task"), sep = "_") %>% inner_join(Subjects)
performance.speech$task <- factor(performance.speech$Task, levels = c("N1","N2","N3","N4"), labels = c("black","red","blue","purple"))

performance_sum <- summarySEwithin2(performance.speech, measurevar = "performance", withinvars = c("Task"), idvar = "subjectid")
performance_sum$Task <- factor(performance_sum$Task, levels = c("N1","N2","N3","N4"), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))
```

### Working Memory

```{r Familiarization_WM, warning = F, message = F}
#Summarizing working memory performance on the N-back across all load levels
##Hit rate, correct rejections
performance.wm <- coged.wm %>% select(subjectid, completed, hitrate_N1, CRrate_N1, hitrate_N2, CRrate_N2, hitrate_N3, CRrate_N3, hitrate_N4, CRrate_N4) %>%
   group_by(subjectid) %>% filter(completed == 1) %>% select(-completed) %>%
  pivot_longer(names_to = "level", values_to = "performance", -c(subjectid)) %>%
  separate(col = level, into=c("Metric","Task"), sep = "_") %>%
  pivot_wider(names_from = Metric, values_from = performance)  %>% inner_join(Subjects)
performance.wm$task <- factor(performance.wm$Task, levels = c("N1","N2","N3","N4"), labels = c("black","red","blue","purple"))

performance.sum.wm <- summarySEwithin2(performance.wm, measurevar = "hitrate", withinvars = c("Task"), idvar = "subjectid")
performance.sum.wm$Task <- factor(performance.sum.wm$Task, levels = c("N1","N2","N3","N4"), labels = c("1-back","2-back","3-back","4-back"))

##RT
performance.wm.RT <- coged.wm.full %>% select(subjectid, blockcode, phase, response, latency) %>% filter(phase == 1) %>%
  rename(task = "blockcode") %>% filter(task != "ratingSummary") %>% filter(response != 0)
performance.wm.RT$task <- factor(performance.wm.RT$task, levels = c("1back","2back","3back","4back"), labels = c("black","red","blue","purple"))

performance.wm.RT.sum <-inner_join(performance.wm.RT, Subjects) %>% group_by(subjectid, task) %>% summarise(meanRT = mean(latency))
```

### Correlation between averaged residuals from models controlling for the effects of task level & performance

```{r residCor, message=F, warning=F}
#Working Memory Cog-ED
#Summarize average performance on N-Back
d.coged.wm.clean <- d.coged.wm %>% select(subjectid, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -subjectid) %>%
   separate(col = tmp, into=c(NA,"task"), sep = "_")

d.coged.wm.partial <- d.coged.wm.clean %>% group_by(subjectid,task) %>% summarise(meanSV = mean(SV)) %>%
  inner_join(performance.wm, by = c("subjectid","task")) %>% inner_join(performance.wm.RT.sum) %>%
  mutate(taskCode = factor(task, levels =c( "black","red","blue","purple"), labels = c(-2,-1,0,1)),
         FArate = 1-CRrate,
         HR_z = scale(hitrate), 
         FAR_z = scale(FArate),
         dPrime = HR_z - FAR_z)

d.coged.wm.partial$taskCode <- as.numeric(d.coged.wm.partial$taskCode)

#Multilevel model predicting SV from N-Back performance measures (e.g., hit rate, correct rejection rate, RT)
m.SV.wm <- brm(data = d.coged.wm.partial, meanSV ~ taskCode + (1 | subjectid),
                       file = "models/m.SV.wm.rds")
summary(m.SV.wm)
bayes_R2(m.SV.wm)

m.SV.wm.partial <- brm(data = d.coged.wm.partial, meanSV ~ taskCode + hitrate + CRrate + meanRT + (1 | subjectid),
                       file = "models/m.SV.wm.partial.rds")
summary(m.SV.wm.partial)
bayes_R2(m.SV.wm.partial)

#create data frame with residuals from multilevel model
subj.resid.wm <- m.SV.wm.partial[["data"]][["subjectid"]] %>% as_tibble()
colnames(subj.resid.wm) <- "subjectid"
res.WM <- residuals(m.SV.wm.partial) %>% as_tibble() %>% select(Estimate)
colnames(res.WM) <- "resid.wm"
res.subj.WM <- cbind(subj.resid.wm, res.WM)

#Speech Cog-ED
#Summarize average performance on speech-in-noise task
d.coged.speech.clean <- d.coged.speech %>% select(subjectid, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -subjectid) %>%
   separate(col = tmp, into=c(NA,"task"), sep = "_")

d.coged.speech.partial <- d.coged.speech.clean %>% group_by(subjectid,task) %>% summarise(meanSV = mean(SV)) %>%
  inner_join(performance.speech, by = c("subjectid","task")) %>%
  mutate(taskCode = factor(task, levels =c("red","blue","purple"), labels = c(-1,0,1)))
d.coged.speech.partial$taskCode <- as.numeric(d.coged.speech.partial$taskCode)

#Multilevel model predicting SV from speech-in-noise task performance measures (e.g., intelligibility)
m.SV.speech <- brm(data = d.coged.speech.partial, meanSV ~ taskCode + (1 | subjectid),
                           file = "models/m.SV.speech.rds")
summary(m.SV.speech)
bayes_R2(m.SV.speech)

m.SV.speech.partial <- brm(data = d.coged.speech.partial, meanSV ~ taskCode + performance + (1 | subjectid),
                           file = "models/m.SV.speech.partial.rds")
summary(m.SV.speech.partial)
bayes_R2(m.SV.speech.partial)

#create data frame with residuals from multilevel model
subj.resid.speech <- m.SV.speech.partial[["data"]][["subjectid"]] %>% as_tibble()
colnames(subj.resid.speech) <- "subjectid"
res.speech <-residuals(m.SV.speech.partial) %>% as_tibble() %>% select(Estimate)
colnames(res.speech) <- "resid.speech"
res.subj.Speech <- cbind(subj.resid.speech, res.speech)

SV.resids <- cbind(res.subj.WM, res.speech) %>% group_by(subjectid) %>%
  summarise(mean.resid.wm = mean(resid.wm), mean.resid.speech = mean(resid.speech))
#Testing for correlation between cognitive effort discounting across working memory & speech domains
#Controlling for task performance
CogED.cor.partial <- cor_test(data = SV.resids, x = "mean.resid.wm", y = "mean.resid.speech",
                              bayesian = TRUE, bayesian_prior = 0.707107)
#Summarize Bayes Factor from correlation controlling for task performance
CogED.cor.partial

#Plot of correlation between working memory & speech comprehension domains controlling for task level & performance
#Not included in manuscript
fig.resid <- ggplot(SV.resids, aes(mean.resid.speech, mean.resid.wm)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(), panel.background = element_blank(),
         axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Speech Comprehension") + ylab("Working Memory")
fig.resid
```

## Stage III of Analysis: Partial Correlation
### Reward Motivation (BIS/BAS, SPSRQ, GRAPES)

``` {r Reward, warning = F, message =  F}
#BIS/BAS
#Importing and cleaning BIS/BAS
BISBAS.clean <- BISBAS %>% select(c(subjectid,completed, BAS_Drive, BAS_Fun, BAS_Reward, BIS)) %>%
  distinct(subjectid, .keep_all=T) %>% mutate(BAS_total = BAS_Drive + BAS_Fun + BAS_Reward)
BISBAS.SV <- inner_join(average.SV, BISBAS.clean)
  
#SPSRQ
#Importing and cleaning SPSRQ
SPSRQ.clean <- SPSRQ %>% select(c(subjectid, completed, SensitivityToReward, SensitivityToPunishment)) %>% 
  distinct(subjectid, .keep_all=T)
SPSRQ.SV <- inner_join(average.SV, SPSRQ.clean)

#GRAPES
#Importing and cleaning GRAPES
GRAPES.clean <- GRAPES %>% select(c(subjectid, ends_with("response"))) %>% distinct(subjectid, .keep_all=T) %>%
  mutate(GRAPES.rew = q1_response + q4_response + q6_response + q7_response + q9_response + q10_response + q15_response +
         q16_response + q16_response + q19_response + q20_response + q21_response + q25_response + q26_response + q27_response,
         GRAPES.pun = q2_response + q3_response + q5_response + q8_response + q11_response + q12_response + q13_response +
         q14_response + q18_response + q22_response + q23_response + q24_response + q28_response + q29_response + q30_response)
GRAPES.SV <- inner_join(average.SV, GRAPES.clean)
```

### Working Memory Capacity (Listing Span, Operation Span, Symmetry Span)

``` {r WMC, warning = F, message =  F}
#Importing and cleaning WMC measures 
#Listening Span
LSpan.clean <- LSpan %>% select(c(subjectid, completed, ListeningSpanScore)) %>%
  distinct(subjectid, .keep_all=T)
LSpan.SV <- inner_join(average.SV, LSpan.clean)

#Operation Span
OSpan.clean <- OSpan %>% select(c(subjectid, completed, ospan)) %>%
  distinct(subjectid, .keep_all=T)
OSpan.SV <- inner_join(average.SV, OSpan.clean)

#Symmetry Span
SymSpan.clean <- SymmSpan %>% select(c(subjectid, completed, sspan)) %>%
  distinct(subjectid, .keep_all=T)
SymSpan.SV <- inner_join(average.SV, SymSpan.clean)
```

### Partial correlation controlling for WMC and reward sensitivity (from residualized SV estimates)

```{r Cor_WMC, warning = F, message = F}
#Create data frame with WMC measures, get z-scores, and create a composite measure
LSpan.comp <- LSpan.SV %>% select(-c(Speech, WM))
LSpan.comp$LSpan.z <- scale(LSpan.comp$ListeningSpanScore)
OSpan.comp <- OSpan.SV %>% select(-c(Speech, WM))
OSpan.comp$OSpan.z <- scale(OSpan.comp$ospan)
SymSpan.comp <- SymSpan.SV %>% select(-c(Speech, WM))
SymSpan.comp$SSpan.z <- scale(SymSpan.comp$sspan)

WMC <- inner_join(LSpan.comp, OSpan.comp, by = "subjectid") %>%
  inner_join(SymSpan.comp, by = "subjectid") %>%
  filter(completed.x == 1) %>% filter(completed.y == 1) %>% filter(completed == 1) %>%
  select(-c("completed.x","completed.y","completed")) %>%
  mutate(WMC.composite = (LSpan.z + OSpan.z + SSpan.z)) %>%
  select(subjectid, WMC.composite)

#Correlating the working memory composite with subjective value in WM domain
WMC.composite.SV <- inner_join(average.SV, WMC, by = "subjectid")
WMC.WMSV.cor <- cor_test(data = WMC.composite.SV, x = "WM", y = "WMC.composite", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
WMC.WMSV.cor

#Correlating the reward composite with subjective value in Speech domain
WMC.SpeechSV.cor <- cor_test(data = WMC.composite.SV, x = "Speech", y = "WMC.composite", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
WMC.SpeechSV.cor

#Create data frame with reward sensitivity measures, get z-scores, and create a composite measure
BISBAS.comp <- BISBAS.SV %>% select(-c(Speech, WM, BAS_Drive, BAS_Fun, BAS_Reward, BIS))
BISBAS.comp$BAS.z <- scale(BISBAS.comp$BAS_total)
SPSRQ.comp <- SPSRQ.SV %>% select(-c(Speech, WM, SensitivityToPunishment))
SPSRQ.comp$SPSRQ.rew.z <- scale(SPSRQ.comp$SensitivityToReward)
GRAPES.comp <- GRAPES.SV %>% select(c(subjectid, GRAPES.rew))
GRAPES.comp$GRAPES.rew.z <- scale(GRAPES.comp$GRAPES.rew)

Reward.composite <- inner_join(BISBAS.comp, SPSRQ.comp, by = "subjectid") %>%
  inner_join(GRAPES.comp, by = "subjectid") %>%
  filter(completed.x == 1) %>% filter(completed.y == 1) %>%
  select(-c("completed.x","completed.y")) %>%
  mutate(Rew.composite = (BAS.z + SPSRQ.rew.z + GRAPES.rew.z)) %>%
  select(subjectid, Rew.composite)

#Correlating the reward composite with subjective value in WM domain
Reward.composite.SV <- inner_join(average.SV, Reward.composite, by = "subjectid")
Reward.WMSV.cor <- cor_test(data = Reward.composite.SV, x = "WM", y = "Rew.composite", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
Reward.WMSV.cor

#Correlating the reward composite with subjective value in Speech domain
Reward.SpeechSV.cor <- cor_test(data = Reward.composite.SV, x = "Speech", y = "Rew.composite", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
Reward.SpeechSV.cor

#Testing for partial correlation between residuals (from stage two) controlling for WMC and reward sensitivity
SV.composite.resid <- inner_join(WMC, Reward.composite, by = "subjectid") %>%
  inner_join(SV.resids, by = "subjectid")
SV.composite.resid.clean <- cbind(SV.composite.resid$WMC.composite, SV.composite.resid$Rew.composite,
                                  SV.composite.resid$mean.resid.speech, SV.composite.resid$mean.resid.wm) %>% as_tibble()
colnames(SV.composite.resid.clean) <- c("WMC", "Reward", "Speech", "WM")

WMC.resid.cor <- cor_test(data = SV.composite.resid.clean, x = "WM", y = "Speech", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
#Summarize Bayes Factor from correlation
WMC.resid.cor

#Correlating WMC and Reward Sensitivity composites
d.composites <- inner_join(WMC, Reward.composite, by = "subjectid")
WMC.Reward.cor <- cor_test(data = d.composites, x = "WMC.composite", y = "Rew.composite", bayesian = TRUE,
                          partial_bayesian = TRUE, bayesian_prior  = 0.707107)
WMC.Reward.cor
```

## Figure 2; correlation between working memory & speech comprehension domains controlling for task level, performance, WMC, and reward sensitivity

```{r test_pcorr, warning=FALSE, message=FALSE}
#WM Cog-ED
d.coged.wm.partial.test <- inner_join(d.coged.wm.partial, WMC, by = "subjectid") %>% inner_join(Reward.composite, by = "subjectid")
m.SV.wm.partial.test <- brm(data = d.coged.wm.partial.test, meanSV ~ taskCode + hitrate + CRrate + meanRT + WMC.composite + Rew.composite + (1 | subjectid), file = "models/m.SV.wm.partial.test.rds")

subj.resid.wm.test <- m.SV.wm.partial.test[["data"]][["subjectid"]] %>% as_tibble()
colnames(subj.resid.wm.test) <- "subjectid"
res.WM.test <- resid(m.SV.wm.partial.test) %>% as_tibble() %>% select(Estimate)
colnames(res.WM.test) <- "resid.wm"
res.subj.WM.test <- cbind(subj.resid.wm.test, res.WM.test)

#Speech Cog-ED
d.coged.speech.partial.test <- inner_join(d.coged.speech.partial, WMC, by = "subjectid") %>% inner_join(Reward.composite, by = "subjectid")
m.SV.speech.partial.test <- brm(data = d.coged.speech.partial.test, meanSV ~ taskCode + performance + WMC.composite + Rew.composite + (1 | subjectid), 
                                file = "models/m.SV.speech.partial.test.rds")

subj.resid.speech.test <- m.SV.speech.partial.test[["data"]][["subjectid"]] %>% as_tibble()
colnames(subj.resid.speech.test) <- "subjectid"
res.speech.test <-residuals(m.SV.speech.partial.test) %>% as_tibble() %>% select(Estimate)
colnames(res.speech.test) <- "resid.speech"
res.subj.Speech.test <- cbind(subj.resid.speech.test, res.speech.test)

SV.resids.test <- cbind(res.subj.WM.test, res.speech.test) %>% group_by(subjectid) %>% summarise(mean.resid.wm = mean(resid.wm), mean.resid.speech = mean(resid.speech))
#Testing for correlation between cognitive effort discounting across working memory & speech domains (controlling for task performance)
CogED.cor.partial.test <- cor_test(data = SV.resids.test, x = "mean.resid.wm", y = "mean.resid.speech", bayesian = TRUE, bayesian_prior = 0.707107)

#Plot of correlation between working memory & speech comprehension domains controlling for task level, performance, WMC, and reward sensitivity
##Figure 2
fig.resid.2 <- ggplot(SV.resids.test, aes(mean.resid.speech, mean.resid.wm)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Speech Comprehension") + ylab("Working Memory")
fig.resid.2
```

## Exploratory Analyses 
### Need for Cognition
### Relationship between average subjective value estimates and NCS scores

``` {r NCS, warning = F, message =  F}
#Importing and cleaning NCS 
NCS.clean <- NCS %>% select(c(subjectid, completed, totalscore)) %>%
              distinct(subjectid, .keep_all=T)

NCS.SV <- inner_join(average.SV, NCS.clean)
NCS.SV$WM.z <- scale(NCS.SV$WM)
NCS.SV$Speech.z <- scale(NCS.SV$Speech)
NCS.SV$NCS.comp <- NCS.SV$WM.z + NCS.SV$Speech.z

#Testing for the correlation between NCS and SV estimates from both WM and Speech comprehension domains 
NCS.wm.cor <- cor_test(data = NCS.SV, x = "WM", y = "totalscore",
                       bayesian = TRUE, bayesian_prior = 0.707107)
NCS.wm.cor
NCS.speech.cor <- cor_test(data = NCS.SV, x = "Speech", y = "totalscore",
                           bayesian = TRUE, bayesian_prior = 0.707107)
NCS.speech.cor
NCS.comp.cor <- cor_test(data = NCS.SV, x = "NCS.comp", y = "totalscore",
                         bayesian = TRUE, bayesian_prior = 0.707107)
NCS.comp.cor

#Testing for the correlation between NCS and SV estimates from both WM and Speech comprehension domains
NCS.SV.resid <- inner_join(SV.resids.test, NCS.clean)
NCS.wm.resid.cor <- cor_test(data = NCS.SV.resid, x = "mean.resid.wm", y = "totalscore",
                             bayesian = TRUE, bayesian_prior = 0.707107)
NCS.wm.resid.cor
NCS.speech.resid.cor <- cor_test(data = NCS.SV.resid, x = "mean.resid.speech", y = "totalscore",
                                 bayesian = TRUE, bayesian_prior = 0.707107)
NCS.speech.resid.cor
```
