---
title: "Domain-general cognitive motivation: evidence from economic decision-making"
author: "JC"
date: "3/24/2021"
output:
  html_document: default
  code_folding: "hide"
---
## 109 YAs

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(lme4); library(BayesFactor); library(bayestestR); library(correlation); library(knitr); library(kableExtra); library(RColorBrewer); library(tidyverse);
source("summarySEwithin2.R")

#Create data directories
#Cog-ED
coged.wm.path<-"~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/CogED/mdd_coged_wm.csv"
coged.speech.path<-"~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/CogED/mdd_coged_speech.csv"
#Individual Difference Questionnaires
NCS.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Questionnaires/MDD_NCS.csv"
SSQ.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Questionnaires/MDD_Ssq.csv"
SPSRQ.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Questionnaires/MDD_Spsrq.csv"
BISBAS.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Questionnaires/MDD_Bisbas.csv"
GRAPES.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Questionnaires/MDD_Grapes.csv"
#Working Memory Capacity
LSpan.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Listening-Span/mdd_listening-span.csv"
OSpan.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/O-Span/mdd_o-span.csv"
SymmSpan.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Symm-Span/MDD_Symm-Span.csv"
#complete subject list
subjects.path <- "~/Box/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/ID-Lists/subjects_online_MDD.csv"
#Make data frames for Cog-ED and demographics info
coged.wm<- read.csv(coged.wm.path, header = T)
coged.speech<- read.csv(coged.speech.path, header = T) 
#Make data frames for individual difference questionnaires 
NCS <- read.csv(NCS.path, header = T)
SSQ <- read.csv(SSQ.path, header = T)
SPSRQ <- read.csv(SPSRQ.path, header = T)
BISBAS <- read.csv(BISBAS.path, header = T)
GRAPES <- read.csv(GRAPES.path, header = T)
#Make data frames for working memory capacity tasks
LSpan <- read.csv(LSpan.path, header = T)
OSpan <- read.csv(OSpan.path, header = T)
SymmSpan <- read.csv(SymmSpan.path, header = T)
#Make data frame for useable subject info
Subjects <- read.csv(subjects.path, header = F)
```


```{r SV_CogED, warning=F, message=F}
#Cog-ED Data
#clean data frame(s) with Cog-ED subjective value (SV) estimates and transform data so that SV estimates are equivalent across both domains (i.e., speech, WM)
d.coged.wm <- coged.wm %>% select(subjectid,completed,fixedAmount_N2_1,fixedAmount_N2_2,fixedAmount_N2_3,fixedAmount_N3_1,fixedAmount_N3_2,
                            fixedAmount_N3_3,fixedAmount_N4_1,fixedAmount_N4_2,fixedAmount_N4_3,
                            IP12_1,IP12_2,IP12_3,IP13_1,IP13_2,IP13_3,IP14_1,IP14_2,IP14_3) %>%
  filter(completed == 1) %>%
  group_by(subjectid) %>%
  mutate(Domain = "WM",
         domainCode = 0,
         SV2_1 = ifelse(fixedAmount_N2_1 == "X", IP12_1/2, ((2-IP12_1)/2)+1),
         SV2_2 = ifelse(fixedAmount_N2_2 == "X", IP12_2/3, ((3-IP12_2)/3)+1),
         SV2_3 = ifelse(fixedAmount_N2_3 == "X", IP12_1/4, ((4-IP12_3)/4)+1),
         SV3_1 = ifelse(fixedAmount_N3_1 == "X", IP13_1/2, ((2-IP13_1)/2)+1),
         SV3_2 = ifelse(fixedAmount_N3_2 == "X", IP13_2/3, ((3-IP13_2)/3)+1),
         SV3_3 = ifelse(fixedAmount_N3_3 == "X", IP13_1/4, ((4-IP13_3)/4)+1),
         SV4_1 = ifelse(fixedAmount_N4_1 == "X", IP14_1/2, ((2-IP14_1)/2)+1),
         SV4_2 = ifelse(fixedAmount_N4_2 == "X", IP14_2/3, ((3-IP14_2)/3)+1),
         SV4_3 = ifelse(fixedAmount_N4_3 == "X", IP14_3/4, ((4-IP14_3)/4)+1),
         SV_red = (SV2_1 + SV2_2 + SV2_3)/3,
         SV_blue = (SV3_1 + SV3_2 + SV3_3)/3,
         SV_purple = (SV4_1 + SV4_2 + SV4_3)/3)

d.coged.speech <- coged.speech %>%
  select(subjectid,completed,fixedAmount_N2_1,fixedAmount_N2_2,fixedAmount_N2_3,fixedAmount_N3_1,
                            fixedAmount_N3_2,fixedAmount_N3_3,fixedAmount_N4_1,fixedAmount_N4_2,fixedAmount_N4_3,
                            IP12_1,IP12_2,IP12_3,IP13_1,IP13_2,IP13_3,IP14_1,IP14_2,IP14_3) %>%
  filter(completed == 1) %>%
  group_by(subjectid) %>%
  mutate(Domain = "Speech",
         domainCode = 1,
         SV2_1 = ifelse(fixedAmount_N2_1 == "X", IP12_1/2, ((2-IP12_1)/2)+1),
         SV2_2 = ifelse(fixedAmount_N2_2 == "X", IP12_2/3, ((3-IP12_2)/3)+1),
         SV2_3 = ifelse(fixedAmount_N2_3 == "X", IP12_1/4, ((4-IP12_3)/4)+1),
         SV3_1 = ifelse(fixedAmount_N3_1 == "X", IP13_1/2, ((2-IP13_1)/2)+1),
         SV3_2 = ifelse(fixedAmount_N3_2 == "X", IP13_2/3, ((3-IP13_2)/3)+1),
         SV3_3 = ifelse(fixedAmount_N3_3 == "X", IP13_1/4, ((4-IP13_3)/4)+1),
         SV4_1 = ifelse(fixedAmount_N4_1 == "X", IP14_1/2, ((2-IP14_1)/2)+1),
         SV4_2 = ifelse(fixedAmount_N4_2 == "X", IP14_2/3, ((3-IP14_2)/3)+1),
         SV4_3 = ifelse(fixedAmount_N4_3 == "X", IP14_3/4, ((4-IP14_3)/4)+1),
         SV_red = (SV2_1 + SV2_2 + SV2_3)/3,
         SV_blue = (SV3_1 + SV3_2 + SV3_3)/3,
         SV_purple = (SV4_1 + SV4_2 + SV4_3)/3)
#Merge WM and Speech Cog-ED data frames
coged.merged <- rbind(d.coged.wm, d.coged.speech)

#Filter out subjects who have not completes all tasks in the protocol
colnames(Subjects) <- "subjectid"
coged.merged <-inner_join(Subjects, coged.merged)

#Add dummy variables (task, domain) for multilevel models
d.coged.SV <- coged.merged %>% select(subjectid,Domain,domainCode, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid,Domain,domainCode)) %>%
  separate(col = tmp, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c("red","blue","purple"), labels=c(-1,0,1)))
d.coged.SV$taskCode <- as.numeric(d.coged.SV$taskCode)
d.coged.SV$domainCode <- as.numeric(d.coged.SV$domainCode)
#Multilevel model of subjective value with task and domain as predictors
m.SV.coged <- lmer(data = d.coged.SV, SV ~ taskCode*domainCode + (1 | subjectid))
summary(m.SV.coged)

#Add dummy variables (task, domain) for multilevel models
d.coged.SV.full <- coged.merged %>% select(subjectid,Domain,domainCode, SV2_1, SV2_2, SV2_3, SV3_1, SV3_2, SV3_3, SV4_1, SV4_2, SV4_3) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid,Domain,domainCode)) %>%
  separate(col = tmp, into=c("Task","Reward"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c("SV2","SV3","SV4"), labels=c(-1,0,1)),
         rewardCode = factor(Reward, levels = c(1,2,3), labels = c(-1,0,1)))
d.coged.SV.full$taskCode <- as.numeric(d.coged.SV.full$taskCode)
d.coged.SV.full$domainCode <- as.numeric(d.coged.SV.full$domainCode)
d.coged.SV.full$rewardCode <- as.numeric(d.coged.SV.full$rewardCode)

#Multilevel model of subjective value with task and domain as predictors
m.SV.coged.full <- lmer(data = d.coged.SV.full, SV ~ taskCode*domainCode*rewardCode + (1 | subjectid))
summary(m.SV.coged.full)
```

## Cognitive Effort Discounting

```{r CogED_Plot, warning = F, message = F}
#Plotting SV estimates
#Create summary stats for group plots
CogED_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Domain"), idvar = "subjectid")
CogED_sum$Task <- factor(CogED_sum$Task, levels = c("red","blue","purple"), labels = c("red","blue","purple"))
CogED_sum$Domain <- factor(CogED_sum$Domain, levels = c("WM","Speech"), labels = c("WM","Speech"))

#Plotting SV across both gain and loss domains
Domain.labs <- c("Speech Comprehension", "Working Memory")
names(Domain.labs) <- c("Speech", "WM")

fig.1 <- ggplot(CogED_sum, aes(x=Task, y=SV, fill=Task, color=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold", size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2, size=1.25) +  
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") +
  facet_wrap(.~ Domain, labeller = labeller(Domain = Domain.labs))
fig.1 + scale_fill_brewer(palette = "Set1",  name="Task Effort Level", labels=c("Low","Medium","High")) + scale_color_brewer(palette = "Set1", name="Task Effort Level",labels=c("Low","Medium","High"))


#Plotting SV estimates
#Create summary stats for group plots
CogED_Rew_sum <- summarySEwithin2(d.coged.SV.full, measurevar = "SV", withinvars = c("Task","Domain","Reward"), idvar = "subjectid")
CogED_Rew_sum$Task <- factor(CogED_Rew_sum$Task, levels = c("SV2","SV3","SV4"), labels = c("Low Effort","Medium Effort","High Effort"))
CogED_Rew_sum$Reward <- factor(CogED_Rew_sum$Reward, levels = c("1","2","3"), labels = c("Low Reward","Medium Reward","High Reward"))
CogED_Rew_sum$Domain <- factor(CogED_Rew_sum$Domain, levels = c("WM","Speech"), labels = c("WM","Speech"))

#Plotting SV across both gain and loss domains
Domain.labs <- c("Speech Comprehension", "Working Memory")
names(Domain.labs) <- c("Speech", "WM")

fig.rew <- ggplot(CogED_Rew_sum, aes(x=Task, y=SV, fill=Task, color=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold", size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2, size=1.25) +  
  scale_x_discrete(breaks=NULL) +
  coord_cartesian(ylim = c(0,1)) +
  xlab("") + ylab("Subjective Value") +
  facet_wrap(.~ Domain + Reward, labeller = labeller(Domain = Domain.labs))
fig.rew + scale_fill_brewer(palette = "Set1",  name="Task Effort Level", labels=c("Low","Medium","High")) + scale_color_brewer(palette = "Set1", name="Task Effort Level",labels=c("Low","Medium","High"))
```

```{r CogED_cor, warning = F, message = F}
#Correlating Average SV (within-subj) across domains
average.SV <- coged.merged %>% select(subjectid, Domain, SV_red, SV_blue, SV_purple) %>%
  group_by(subjectid, Domain) %>%
  dplyr::summarise(SV_avg = (SV_red + SV_blue + SV_purple)/3) %>%
  pivot_wider(values_from = "SV_avg", names_from = "Domain")

#Testing for correlation between cognitive effort discounting across working memory & speech domains
CogED.cor <- cor_test(data = average.SV, x = "Speech", y = "WM", bayesian = TRUE, bayesian_prior = 0.707107)
describe_posterior(CogED.cor, ci = .95)
#Summarize Bayes Factor from correlation
CogED.cor

#Plot of correlation between working memory & speech comprehension domains (Figure 2)
fig.2 <- ggplot(average.SV, aes(Speech, WM)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Speech Comprehension") + ylab("Working Memory")
fig.2 
```

## Removing Participants who have an average SV >1

```{r CogED_cor, warning = F, message = F}
#Correlating Average SV (within-subj) across domains
average.SV.outliers <- coged.merged %>% select(subjectid, Domain, SV_red, SV_blue, SV_purple) %>%
  group_by(subjectid, Domain) %>%
  dplyr::summarise(SV_avg = (SV_red + SV_blue + SV_purple)/3) %>%
  pivot_wider(values_from = "SV_avg", names_from = "Domain") %>%
  filter(Speech < 1) %>% filter(WM < 1)

#Testing for correlation between cognitive effort discounting across working memory & speech domains
CogED.cor.adj <- cor_test(data = average.SV.outliers, x = "Speech", y = "WM", bayesian = TRUE, bayesian_prior = 0.707107)
describe_posterior(CogED.cor.adj, ci = .95)
#Summarize Bayes Factor from correlation
CogED.cor.adj

#Plot of correlation between working memory & speech comprehension domains (Figure 2)
fig.outlier.rm <- ggplot(average.SV.outliers, aes(Speech, WM)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("Reverse Discounters Removed") +
    xlab("Speech Comprehension") + ylab("Working Memory")
fig.outlier.rm 
```

## NASA TLX
#### Participants completed NASA ratings after each load level during the familiarization phase (likert scale: 1-21; higher values indicate greater endorsement)

```{r Self-Report, warning = F, message = F}
#Mental Demand Ratings
NASA.m.demand.wm <- coged.wm %>% select(subjectid, completed, mentaldemand_1, mentaldemand_2, mentaldemand_3, mentaldemand_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "WM")

NASA.m.demand.speech <- coged.speech %>% select(subjectid, completed, mentaldemand_1, mentaldemand_2, mentaldemand_3, mentaldemand_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "Speech")

NASA.m.demand <- rbind(NASA.m.demand.wm,NASA.m.demand.speech) %>% select(-completed) %>%
  pivot_longer(names_to = "mental_demand", values_to = "rating", -c(subjectid,Domain)) %>%
  separate(col = mental_demand, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c(1,2,3,4), labels=c(0,1,2,3)),
          domainCode = factor(Domain, levels = c("WM","Speech"), labels = c(0,1)))

NASA.m.demand$taskCode <- as.numeric(NASA.m.demand$taskCode)
NASA.m.demand$domainCode <- as.numeric(NASA.m.demand$domainCode)
NASA_mdemand_sum <- summarySEwithin2(NASA.m.demand, measurevar = "rating", withinvars = c("Task","Domain"), idvar = "subjectid")
NASA_mdemand_sum$Task <- factor(NASA_mdemand_sum$Task, levels = c(1,2,3,4), labels = c("black","red","blue","purple"))

m.mentalDemand <- lmer(data = NASA.m.demand, rating ~ taskCode*domainCode + (1 | subjectid))
summary(m.mentalDemand)

p.m.demand <- ggplot(NASA_mdemand_sum, aes(x=Task, y=rating, fill=Domain)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Mental Demand") + ggtitle("Self-Reported Mental Demand") 
p.m.demand + labs(fill = "Domain") + scale_fill_brewer(palette = "Paired")

#Frustration Ratings
NASA.frust.wm <- coged.wm %>% select(subjectid, completed, frustration_1, frustration_2, frustration_3, frustration_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "WM")
 
NASA.frust.speech <- coged.speech %>% select(subjectid, completed, frustration_1, frustration_2, frustration_3, frustration_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "Speech") 
  
NASA.frust <- rbind(NASA.frust.wm,NASA.frust.speech) %>% select(-completed) %>%
  pivot_longer(names_to = "frustration", values_to = "rating", -c(subjectid, Domain)) %>%
  separate(col = frustration, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c(1,2,3,4), labels=c(0,1,2,3)),
          domainCode = factor(Domain, levels = c("WM","Speech"), labels = c(0,1)))
NASA.frust$taskCode <- as.numeric(NASA.frust$taskCode)
NASA.frust$domainCode <- as.numeric(NASA.frust$domainCode)

m.Frustration <- lmer(data = NASA.frust, rating ~ taskCode*domainCode + (1 | subjectid))
summary(m.Frustration)

NASA_frust_sum <- summarySEwithin2(NASA.frust, measurevar = "rating", withinvars = c("Task","Domain"), idvar = "subjectid")
NASA_frust_sum$Task <- factor(NASA_frust_sum$Task, levels = c(1,2,3,4), labels = c("black","red","blue","purple"))

p.frust <- ggplot(NASA_frust_sum, aes(x=Task, y=rating, fill=Domain)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Frustration") + ggtitle("Self-Reported Frustration") 
p.frust +  labs(fill = "Domain") + scale_fill_brewer(palette = "Paired")

#Effort Ratings
NASA.effort.wm <- coged.wm %>% select(subjectid, completed, effort_1, effort_2, effort_3, effort_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "WM")

NASA.effort.speech <- coged.speech %>% select(subjectid, completed, effort_1, effort_2, effort_3, effort_4) %>%
  group_by(subjectid) %>%
  filter(completed == 1) %>%
  mutate(Domain = "Speech") 
  
NASA.effort <- rbind(NASA.effort.wm,NASA.effort.speech) %>% select(-completed) %>%
  pivot_longer(names_to = "effort", values_to = "rating", -c(subjectid,Domain)) %>%
  separate(col = effort, into=c(NA,"Task"), sep = "_") %>%
    mutate(taskCode = factor(Task, levels=c(1,2,3,4), labels=c(0,1,2,3)),
          domainCode = factor(Domain, levels = c("WM","Speech"), labels = c(0,1)))
NASA.effort$taskCode <- as.numeric(NASA.effort$taskCode)
NASA.effort$domainCode <- as.numeric(NASA.effort$domainCode)

m.Effort <- lmer(data = NASA.effort, rating ~ taskCode*domainCode + (1 | subjectid))
summary(m.Effort)

NASA_effort_sum <- summarySEwithin2(NASA.effort, measurevar = "rating", withinvars = c("Task","Domain"), idvar = "subjectid")
NASA_effort_sum$Task <- factor(NASA_effort_sum$Task, levels = c(1,2,3,4), labels = c("black","red","blue","purple"))

p.effort <- ggplot(NASA_effort_sum, aes(x=Task, y=rating, fill=Domain)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Effort") + ggtitle("Self-Reported Effort") 
p.effort + labs(fill = "Domain") + scale_fill_brewer(palette = "Paired")
```

## Familiarization Phase Performance
### Speech
```{r Familiarization_Speech, warning = F, message = F}
performance.speech <- coged.speech %>% select(subjectid, completed, percentCorrect_N1, percentCorrect_N2, percentCorrect_N3, percentCorrect_N4) %>%
   group_by(subjectid) %>% filter(completed == 1) %>% select(-completed) %>%
  pivot_longer(names_to = "level", values_to = "performance", -c(subjectid)) %>%
  separate(col = level, into=c(NA,"Task"), sep = "_") 

performance_sum <- summarySEwithin2(performance.speech, measurevar = "performance", withinvars = c("Task"), idvar = "subjectid")
performance_sum$Task <- factor(performance_sum$Task, levels = c("N1","N2","N3","N4"), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))

performance.table <- kable(performance_sum %>% select(!contains("Normed")), caption = "Mean Accuracy of Keywords across Load Levels") %>%  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
performance.table
```

### Working Memory
```{r Familiarization_WM, warning = F, message = F}
performance.wm <- coged.wm%>% select(subjectid, completed, hitrate_N1, CRrate_N1, hitrate_N2, CRrate_N2, hitrate_N3, CRrate_N3, hitrate_N4, CRrate_N4) %>%
   group_by(subjectid) %>% filter(completed == 1) %>% select(-completed) %>%
  pivot_longer(names_to = "level", values_to = "performance", -c(subjectid)) %>%
  separate(col = level, into=c("Metric","Task"), sep = "_") %>%
  pivot_wider(names_from = Metric, values_from = performance)
performance.wm$task <- factor(performance.wm$Task, levels = c("N1","N2","N3","N4"), labels = c("black","red","blue","purple"))

performance.sum.wm <- summarySEwithin2(performance.wm, measurevar = "hitrate", withinvars = c("Task"), idvar = "subjectid")
performance.sum.wm$Task <- factor(performance.sum.wm$Task, levels = c("N1","N2","N3","N4"), labels = c("1-back","2-back","3-back","4-back"))

performance.table.wm <- kable(performance.sum.wm %>% select(!contains("Normed")), caption = "Hit rate across Load Levels") %>%  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
performance.table.wm
```

## Individual Difference Questionnaires
### Need for Cognition

``` {r NCS, warning = F, message =  F}
#Importing and cleaning NCS 
NCS.clean <- NCS %>% select(c(subjectid, completed, totalscore)) %>%
              distinct(subjectid, .keep_all=T)

NCS.SV <- inner_join(average.SV, NCS.clean)
```

### Speech Self-Report (SSQ)

``` {r SSQ, warning = F, message =  F}
#Importing and cleaning SSQ 
SSQ.clean <- SSQ %>% select(c(subject, ends_with("response"))) %>% distinct(subject, .keep_all=T) %>%
  mutate(SSQ.total = rowSums(.[2:16]),
         SSQ.speech = rowSums(.[2:6]),
         SSQ.spatial = rowSums(.[7:11]),
         SSQ.quality = rowSums(.[12:16])) %>%
  rename(subjectid = "subject") %>%
  select(subjectid, SSQ.total, SSQ.speech, SSQ.spatial, SSQ.quality)

SSQ.SV <- inner_join(average.SV, SSQ.clean)
```

### Reward Motivation (BIS/BAS, SPSRQ, GRAPES)

``` {r Reward, warning = F, message =  F}
#BIS/BAS
#Importing and cleaning BIS/BAS
BISBAS.clean <- BISBAS %>% select(c(subjectid,completed, BAS_Drive, BAS_Fun, BAS_Reward, BIS)) %>% distinct(subjectid, .keep_all=T) %>% mutate(BAS_total = BAS_Drive + BAS_Fun + BAS_Reward)
BISBAS.SV <- inner_join(average.SV, BISBAS.clean)
  
#SPSRQ
#Importing and cleaning SPSRQ
SPSRQ.clean <- SPSRQ %>% select(c(subjectid, completed, SensitivityToReward, SensitivityToPunishment)) %>% distinct(subjectid, .keep_all=T)
SPSRQ.SV <- inner_join(average.SV, SPSRQ.clean)

#GRAPES
GRAPES.clean <- GRAPES %>% select(c(subject, ends_with("response"))) %>% distinct(subject, .keep_all=T) %>%
  mutate(GRAPES.rew = q1_response + q4_response + q6_response + q7_response + q9_response + q10_response + q15_response +
         q16_response + q16_response + q19_response + q20_response + q21_response + q25_response + q26_response + q27_response,
         GRAPES.pun = q2_response + q3_response + q5_response + q8_response + q11_response + q12_response + q13_response +
         q14_response + q18_response + q22_response + q23_response + q24_response + q28_response + q29_response + q30_response) %>%
  rename(subjectid = "subject")
GRAPES.SV <- inner_join(average.SV, GRAPES.clean)
```

### Working Memory Capacity (Listing Span, Operation Span, Symmetry Span)

``` {r WMC, warning = F, message =  F}
#Importing and cleaning WMC measures 
#Listening Span
LSpan.clean <- LSpan %>% select(c(subjectid, completed, ListeningSpanScore)) %>% distinct(subjectid, .keep_all=T)
LSpan.SV <- inner_join(average.SV, LSpan.clean)

#Operation Span
OSpan.clean <- OSpan %>% select(c(subjectid, completed, ospan)) %>% distinct(subjectid, .keep_all=T)
OSpan.SV <- inner_join(average.SV, OSpan.clean)

#Symmetry Span
SymSpan.clean <- SymmSpan %>% select(c(subjectid, completed, sspan)) %>% distinct(subjectid, .keep_all=T)
SymSpan.SV <- inner_join(average.SV, SymSpan.clean)
```

##Stage II of Analysis--Partialing out task performance on SV

```{r partialCorr, message=F, warning=F}
#Working Memory Cog-ED
#Summarize average performance on N-Back
d.coged.wm.clean <- d.coged.wm %>% select(subjectid, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -subjectid) %>%
   separate(col = tmp, into=c(NA,"task"), sep = "_")

d.coged.wm.partial <- d.coged.wm.clean %>% group_by(subjectid,task) %>% summarise(meanSV = mean(SV)) %>%
  inner_join(performance.wm, by = c("subjectid","task")) %>%
  mutate(taskCode = factor(task, levels =c( "black","red","blue","purple"), labels = c(-2,-1,0,1)))
d.coged.wm.partial$taskCode <- as.numeric(d.coged.wm.partial$taskCode)

m.SV.wm.partial <- lmer(data = d.coged.wm.partial, meanSV ~ taskCode + hitrate + CRrate + (1 | subjectid))
summary(m.SV.wm.partial)
head(residuals(m.SV.wm.partial))

res.WM <- resid(m.SV.wm.partial) %>% as_tibble()

#Speech Cog-ED
d.coged.speech.partial <- d.coged.speech %>% group_by(subjectid,task) %>% summarise(meanSV = mean(SV)) %>%
  inner_join(speech.subj, by = c("subjectid","task")) %>%
  mutate(taskCode = factor(task, levels =c("Red","Blue","Purple"), labels = c(-1,0,1)))
d.coged.speech.partial$taskCode <- as.numeric(d.coged.speech.partial$taskCode)

m.SV.speech.partial <- lmer(data = d.coged.speech.partial, meanSV ~ taskCode + intelligibility + (1 | subID))
summary(m.SV.speech.partial)
augment(m.SV.speech.partial)
res.speech <-residuals(m.SV.speech.partial) %>% as_tibble()

#Testing for correlation between cognitive effort discounting across working memory & speech domains (controlling for task performance)
CogED.cor.partial <- correlationBF(x = res.WM$Estimate, y = res.speech$Estimate, rscale = 0.707107)
describe_posterior(CogED.cor.partial, ci = .95)
#Summarize Bayes Factor from correlation controlling for task performance
CogED.cor.partial
```

##Stage III of Analysis--Controlling for WMC and Reward Motivation

```{r Corr_WMC, warning = F, message = F}
#Create data frame with WMC measures, get z-scores, and create a composite measure
LSpan.comp <- LSpan.SV %>% select(-c(Speech, WM))
LSpan.comp$LSpan.z <- scale(LSpan.comp$ListeningSpanScore)
OSpan.comp <- OSpan.SV %>% select(-c(Speech, WM))
OSpan.comp$OSpan.z <- scale(OSpan.comp$ospan)
SymSpan.comp <- SymSpan.SV %>% select(-c(Speech, WM))
SymSpan.comp$SSpan.z <- scale(SymSpan.comp$sspan)

WMC <- inner_join(LSpan.comp, OSpan.comp, by = "subjectid") %>% inner_join(SymSpan.comp, by = "subjectid") %>%
  filter(completed.x == 1) %>% filter(completed.y == 1) %>% filter(completed == 1) %>%
  select(-c("completed.x","completed.y","completed")) %>%
  mutate(WMC.composite = (LSpan.z + OSpan.z + SSpan.z)) %>%
  select(subjectid, WMC.composite)

#Create data frame with reward sensitivity measures, get z-scores, and create a composite measure
BISBAS.comp <- BISBAS.SV %>% select(-c(Speech, WM, BAS_Drive, BAS_Fun, BAS_Reward, BIS))
BISBAS.comp$BAS.z <- scale(BISBAS.comp$BAS_total)
SPSRQ.comp <- SPSRQ.SV %>% select(-c(Speech, WM, SensitivityToPunishment))
SPSRQ.comp$SPSRQ.rew.z <- scale(SPSRQ.comp$SensitivityToReward)
GRAPES.comp <- GRAPES.SV %>% select(c(subjectid, GRAPES.rew))
GRAPES.comp$GRAPES.rew.z <- scale(GRAPES.comp$GRAPES.rew)

Reward.composite <- inner_join(BISBAS.comp, SPSRQ.comp, by = "subjectid") %>% inner_join(GRAPES.comp, by = "subjectid") %>%
  filter(completed.x == 1) %>% filter(completed.y == 1) %>%
  select(-c("completed.x","completed.y")) %>%
  mutate(Rew.composite = (BAS.z + SPSRQ.rew.z + GRAPES.rew.z)) %>%
  select(subjectid, Rew.composite)

#Testing for correlation between WMC Composite and N-Back Familiarization Phase Performance
SV.composite <- inner_join(WMC, Reward.composite, by = "subjectid") %>% inner_join(average.SV, by = "subjectid")

SV.composite.clean <- cbind(SV.composite$WMC.composite, SV.composite$Rew.composite, SV.composite$Speech, SV.composite$WM) %>% as_tibble()

colnames(SV.composite.clean) <- c("WMC", "Reward", "Speech", "WM")

WMC.cor <- cor_test(data = SV.composite.clean, x = "WM", y = "Speech", bayesian = TRUE, partial_bayesian = TRUE, bayesian_prior  = 0.707107)

WMC.cor.plot <- SV.composite.clean %>% correlation(partial = TRUE) %>% plot()
#Summarize Bayes Factor from correlation


#Plot of correlation between working memory & speech comprehension domains (Figure 2)
fig.WMC <- ggplot(WMC.NBack, aes(HR, WMC.composite)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Average Hit Rate (N-Back)") + ylab("WMC Composite Score")
fig.WMC
```
