---
title: "Speech CogED Online"
author: "JC"
date: "1/08/2021"
output:
  html_document: default
  code_folding: "hide"
---
#Online Cog-ED Speech Pilots (30 YAs; ages 20-40)

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(lme4); library(knitr); library(kableExtra); library(RColorBrewer); library(tidyverse);
source("summarySEwithin2.R")

#Create data directories
coged.path<-"~/Box Sync/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Pilots/coged_speech_0108.csv"
PTQ.path <- "~/Box Sync/CCPLab_Aging_Studies/Multi-Domain-Discounting/Data/Online/Pilots/speech_coged_ptq__0108.csv"

#Make data frames for Cog-ED and demographics info
coged<- read.csv(coged.path, header = T)
PTQ <- read.csv(PTQ.path, header = T)
```

```{r SV_CogED, warning=F, message=F}
#clean data frame with Cog-ED SV estimates and transform data across so that SV estimates are equivalent across both domains (i.e., gain, loss)
d.coged <- coged %>% select(subjectid, groupid, IP12_1, IP12_2, IP12_3, IP13_1, IP13_2, IP13_3, IP14_1, IP14_2, IP14_3, 
                            percentCorrect_N1, percentCorrect_N2, percentCorrect_N3, percentCorrect_N4) %>%
  group_by(subjectid) %>%
  mutate(SV_red = (IP12_1/2 + IP12_2/3 + IP12_3/4)/3,
         SV_blue = (IP13_1/2 + IP13_2/3 + IP13_3/4)/3,
         SV_purple = (IP14_1/2 + IP14_2/3 + IP14_3/4)/3)

d.coged.SV <- d.coged %>% select(subjectid, SV_red, SV_blue, SV_purple) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid)) %>%
  separate(col = tmp, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c("red","blue","purple"), labels=c(-1,0,1)))
d.coged.SV$taskCode <- as.numeric(d.coged.SV$taskCode)
```

##Cognitive Effort Discounting

``` {r CogED_Plot, warning = F, message = F}
CogED_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task"), idvar = "subjectid")
CogED_sum$Task <- factor(CogED_sum$Task, levels = c("red","blue","purple"), labels = c("-4 SNR","-8 SNR","-12 SNR"))

d.coged.SV$Task <- factor(d.coged.SV$Task, levels = c("red","blue","purple"), labels = c("-4 SNR","-8 SNR","-12 SNR"))
#Plotting SV across both gain and loss domains
p.1 <- ggplot(CogED_sum, aes(x=Task, y=SV, fill=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge(), alpha = .6) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2) + 
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") + ggtitle("Cognitive Effort Discounting")
p.1 + scale_fill_brewer(palette = "Set1") + scale_color_brewer(palette = "Set1")


p.2 <- ggplot(CogED_sum, aes(x=Task, y=SV)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2) + 
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, group=subjectid),
             stat="identity", alpha=0.7) +
  geom_line(data = d.coged.SV, aes(x=Task, y=SV, group=subjectid, colour = factor(subjectid)), alpha = .5) +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("Task") + ylab("Subjective Value") + ggtitle("Cognitive Effort Discounting")
p.CogED <- p.2 + guides(colour=FALSE) 
p.CogED
```

##NASA TLX
####Participants completed NASA ratings after each load level during the familiarization phase (likert scale: 1-21; higher values indicate greater endorsement)

``` {r Self-Report, warning = F, message = F}
#Mental Demand Ratings
NASA.m.demand <- coged %>% select(subjectid, mentaldemand_1, mentaldemand_2, mentaldemand_3, mentaldemand_4) %>%
  group_by(subjectid) %>%
  pivot_longer(names_to = "mental_demand", values_to = "rating", -c(subjectid)) %>%
  separate(col = mental_demand, into=c(NA,"Task"), sep = "_") 
NASA_mdemand_sum <- summarySEwithin2(NASA.m.demand, measurevar = "rating", withinvars = c("Task"), idvar = "subjectid")
NASA_mdemand_sum$Task <- factor(NASA_mdemand_sum$Task, levels = c(1,2,3,4), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))

p.m.demand <- ggplot(NASA_mdemand_sum, aes(x=Task, y=rating)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Mental Demand") + ggtitle("Self-Reported Mental Demand") 
p.m.demand

#Frustration Ratings
NASA.frust <- coged %>% select(subjectid, frustration_1, frustration_2, frustration_3, frustration_4) %>%
  group_by(subjectid) %>%
  pivot_longer(names_to = "frustration", values_to = "rating", -c(subjectid)) %>%
  separate(col = frustration, into=c(NA,"Task"), sep = "_") 
NASA_frust_sum <- summarySEwithin2(NASA.frust, measurevar = "rating", withinvars = c("Task"), idvar = "subjectid")
NASA_frust_sum$Task <- factor(NASA_frust_sum$Task, levels = c(1,2,3,4), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))

p.frust <- ggplot(NASA_frust_sum, aes(x=Task, y=rating)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Frustration") + ggtitle("Self-Reported Frustration") 
p.frust

#Effort Ratings
NASA.effort <- coged %>% select(subjectid, effort_1, effort_2, effort_3, effort_4) %>%
  group_by(subjectid) %>%
  pivot_longer(names_to = "effort", values_to = "rating", -c(subjectid)) %>%
  separate(col = effort, into=c(NA,"Task"), sep = "_") 
NASA_effort_sum <- summarySEwithin2(NASA.effort, measurevar = "rating", withinvars = c("Task"), idvar = "subjectid")
NASA_effort_sum$Task <- factor(NASA_effort_sum$Task, levels = c(1,2,3,4), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))

p.effort <- ggplot(NASA_effort_sum, aes(x=Task, y=rating)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Effort") + ggtitle("Self-Reported Effort") 
p.effort
```

##Familiarization Phase Performance

``` {r Familiarization, warning = F, message = F}
performance <- coged %>% select(subjectid, percentCorrect_N1, percentCorrect_N2, percentCorrect_N3, percentCorrect_N4) %>%
   group_by(subjectid) %>%
  pivot_longer(names_to = "level", values_to = "performance", -c(subjectid)) %>%
  separate(col = level, into=c(NA,"Task"), sep = "_") 

performance_sum <- summarySEwithin2(performance, measurevar = "performance", withinvars = c("Task"), idvar = "subjectid")
performance_sum$Task <- factor(performance_sum$Task, levels = c("N1","N2","N3","N4"), labels = c("0 SNR","-4 SNR","-8 SNR","-12 SNR"))

performance.table <- kable(performance_sum %>% select(!contains("Normed")), caption = "Mean Accuracy of Keywords across Load Levels") %>%  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
performance.table
```

##Post-Task Questionnaire
####Participants completed post-task ratings at the conclusion of the experiment (likert scale: 1-10)

###Avoidance = To what degree did you choose the easier task because you wanted to avoid difficulty?

###Caring = To what degree did you select tasks based on whether or not you would be able to win (or lose) money?

###Challenge = To what degree did you choose the harder task because you wanted to challenge yourself?

###Difficulty = To what degree were your choices based on the difficulty of each task?

###Effort = To what degree were your choices based on the amount of effort each task required?

###Maintenance = To what degree did you select tasks based on whether or not you would be able to maintain your effort?

###Money = To what degree were your choices based on the offer amount ($) of each task?

``` {r PTQ, warning = F, message = F}
PTQ.clean <- PTQ %>%  select(subject, ends_with("response")) %>% select(!contains("strat")) %>% select(!contains("listening")) %>%
  pivot_longer(names_to = "dimension", values_to = "rating", -subject) %>%
  separate(col = dimension, into=c("dimension",NA), sep = "_")
 
PTQ_sum <- summarySEwithin2(PTQ.clean, measurevar = "rating", withinvars = c("dimension"), idvar = "subject")
  
p.PTQ <- ggplot(PTQ_sum, aes(x=dimension, y=rating)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("") + ylab("") + ggtitle("Post-Task Questionnaire") 
p.PTQ
```

###Self-Reported Strategies

``` {r PTQ_strat, warning = F, message = F}
#self-reported strategies
PTQ.strat.subset <- PTQ %>% select(contains("strat")) %>% select(!contains("latency"))
kable(PTQ.strat.subset)
```
